---
title: 'Analysis for Epistemic Overconfidence in Algorithmic News Selection Paper'
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(printr)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Load Data](#load-data)
- [Analysis](#analysis)
  - [H1: Direct Effect of UGT on Algorithmic Appreciation](#h1:-direct-effect-of-ugt-on-algorithmic-appreciation)
  - [H2: Interaction UGT * Epistemic Overconfidence](#h2:-interaction-ugt-*-epistemic-overconfidence)
  - [Predicted Effects](#predicted-effects)
- [Exploratory Analyses](#exploratory-analyses)

## Required Packages &amp; Reproducibility
```{r, message=FALSE, warning=F}
rm(list=ls())

renv::snapshot()

source("../lib/functions.R")
```

## Load Data
```{r}
load("../../data/intermediate/cleaned_data.RData") 
df <- df %>%
  mutate(esc = round(esc, 0),
         ent = round(ent, 0),
         hs = round(hs, 0),
         pt = round(pt, 0),
         surv = round(surv, 0))
#  pid = factor(pid, levels = c("None", "Other", "Democrat",
#                                      "Republican")))
```

## Analysis

### H1: Direct Effect of UGT on Algorithmic Appreciation

```{r, echo=F, fig.width=10, fig.height=10}
df %>%
  select(ent, esc, hs, pt, surv, algo_app) %>%
  pivot_longer(cols = ent:surv) %>%
  mutate(name = recode(name,
                       `ent` = "Entertainment",
                       `esc` = "Escapism",
                       `hs` = "Habit Strength",
                       `pt` = "Passing Time",
                       `surv` = "Surveillance")) %>%
  ggplot(aes(x = value, y = algo_app)) +
  geom_smooth(colour = "#000004FF", fill = "#FCFDBFFF", size = .7) +
  labs(x = "Levels of Gratifications of the News", 
       y = "Levels of Algorithmic Appreciation",
       title = "Bivariate Relationship") +
  facet_wrap(.~name, ncol = 2, scales = "free") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())

```

```{r}
#df <- within(df, pid <- relevel(pid, ref = "Other"))
H1 <- lm(algo_app ~ esc + ent + hs + pt + surv +
           eo + factor(missing_eo) + news + polef + trust +
           age + factor(gender) + factor(country),  data = df)

```

```{r, echo=F}
H1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght",
                       "UGT: Passing Time", 
                       "UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                        "Age","Gender: Male",
                       "Country: US")) %>%
  select(-term) %>%
  ggplot(aes(y = variable)) +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(H1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  ggtitle("DV: Algorithmic Appreciation") +
  theme(plot.title = element_text(hjust = 0.5))
rm(H1)
```

### H2: Interaction UGT * Epistemic Overconfidence

```{r}
H2_1 <-  lm(algo_app ~ esc *eo + ent + hs + pt + surv +
            missing_eo + news + polef + trust + age +
            factor(gender) + factor(country),  data = df)

H2_2 <-  lm(algo_app ~ esc + ent*eo + hs + pt + surv +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

H2_3 <-  lm(algo_app ~ esc + ent + hs*eo + pt + surv +
              factor(missing_eo) + news + polef + trust +
              age + factor(gender) + factor(country),  data = df)

H2_4 <-  lm(algo_app ~ esc + ent + hs + pt*eo + surv +
              factor(missing_eo) + news + polef + trust + 
              age + factor(gender) + factor(country),  data = df)

H2_5 <-  lm(algo_app ~ esc + ent + hs + pt + surv*eo +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

#stargazer::stargazer(H1, H2_1, H2_2, H2_3, H2_4, H2_5,
#                     type = "latex", title="Results", align=TRUE,
#                     star.char = c("+", "*", "**", "***"),
#                     star.cutoff = c(.1, .05, .01, .001),
#                     dep.var.labels = c("Algorithmic Appreciation"),  
#          covariate.labels = c("UGT: Escapism", "UGT: Entertainment", 
#                               "UGT: Habit Strength", "UGT: Passing Time", 
#                               "UGT: Surveillance", "Epistemic Overconfidence (EO)",
#                               "Missing Values: EO", "News Usage", 
#                               "Political Efficacy", "Trust in Media",
#                               "Age", "Gender: Male", "Country: US", 
#                               "Interaction UGT * EO"))
```

```{r, echo=F, fig.width=10, fig.height=10}
f2_1 <- H2_1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "Epistemic Overconfidence", 
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Escapism * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_2 <- H2_2  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment",
                       "Epistemic Overconfidence", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Entertainment * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_3 <- H2_3  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "Epistemic Overconfidence",
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Habit Strength * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_4 <- H2_4  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time",
                       "Epistemic Overconfidence","UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Passing Time * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_5 <- H2_5  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time","UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Surveillance * Epistemic Overconfidence", 14)) %>%
  select(-term)

rbind(f2_1, f2_2, f2_3, f2_4, f2_5) %>%
  ggplot(aes(y = variable)) +
  facet_wrap(~ id, ncol = 2, scales = "free") +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(H2_1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  ggtitle("DV: Algorithmic Appreciation") +
  theme(plot.title = element_text(hjust = 0.5))
rm(f2_1, f2_2, f2_3, f2_4, f2_5)
```

### Predicted Effects
```{r, echo=FALSE,fig.width=10, fig.height=10}
mg1 <- ggpredict(H2_1, terms = c("esc[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Escapism")
mg2 <- ggpredict(H2_2, terms = c("ent[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Entertainment")
mg3 <- ggpredict(H2_3, terms = c("hs[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Habit Strength")
mg4 <- ggpredict(H2_4, terms = c("pt[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Passing Time")
mg5 <- ggpredict(H2_5, terms = c("surv[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Surveillance")

rbind(mg1, mg2, mg3, mg4, mg5) %>%
  mutate(group = recode(group, 
                        `-1` = "Insecure",
                        `2` = "Not Overconfident",
                        `4` = "Overconfident")) %>%
  ggplot(aes(x = x, y = predicted, colour = group)) +
  geom_line() +
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill = group), alpha=0.15) +
  labs(x = "Levels of Gratifications of the News", 
       y = "Predicted Effects on DV for Levels of Overconfidence",
       title = "DV: Algorithmic Appreciation") +
  facet_wrap(.~id, ncol = 2, scales = "free") +
  theme_minimal() +
  scale_fill_viridis(option = "magma", discrete = T) +
  scale_color_viridis(option = "magma", discrete = T) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())
```

## Exploratory Analyses

### Is Relationship between UGT and Epistemic Overconfidence Conditional upon Gender

```{r, echo=FALSE,fig.width=10, fig.height=15}
mg1 <- ggpredict(H2_1, terms = c("esc[1:7]", "eo[-1, 2,4]",
                                 "gender")) %>%
  mutate(id = "Escapism")
mg2 <- ggpredict(H2_2, terms = c("ent[1:7]", "eo[-1, 2,4]",
                                 "gender")) %>%
  mutate(id = "Entertainment")
mg3 <- ggpredict(H2_3, terms = c("hs[1:7]", "eo[-1, 2,4]",
                                 "gender")) %>%
  mutate(id = "Habit Strength")
mg4 <- ggpredict(H2_4, terms = c("pt[1:7]", "eo[-1, 2,4]",
                                 "gender")) %>%
  mutate(id = "Passing Time")
mg5 <- ggpredict(H2_5, terms = c("surv[1:7]", "eo[-1, 2,4]",
                                 "gender")) %>%
  mutate(id = "Surveillance")

rbind(mg1, mg2, mg3, mg4, mg5) %>%
  mutate(group = recode(group, 
                        `-1` = "Insecure",
                        `2` = "Not Overconfident",
                        `4` = "Overconfident")) %>%
  ggplot(aes(x = x, y = predicted, colour = group)) +
  geom_line() +
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill = group), alpha=0.15) +
  labs(x = "Levels of Gratifications of the News", 
       y = "Predicted Effects on DV for Levels of Overconfidence",
       title = "DV: Algorithmic Appreciation") +
  facet_grid(id~facet, scales = "free") +
  theme_minimal() +
  scale_fill_viridis(option = "magma", discrete = T) +
  scale_color_viridis(option = "magma", discrete = T) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())
rm(H2_1, H2_2, H2_3, H2_4, H2_5, 
   mg1, mg2, mg3, mg4, mg5)
```


### Relationship between Appreciation for News Selector and Trust in Media
```{r, echo=F, fig.width=10, fig.height=10}
df %>%
  select(trust, algo_app, own_select, jou_select) %>%
  pivot_longer(cols = algo_app:jou_select) %>%
  mutate(name = recode(name,
                       `jou_select` = "Let journalist choose news for me",
                       `own_select` = "I select my own news",
                       `algo_app` = "Let algorithm choose news for me"),
         name = factor(name, 
                       levels = c("Let journalist choose news for me",
                                  "I select my own news",
                                  "Let algorithm choose news for me"))) %>%
  ggplot(aes(x = value, y = trust)) +
  geom_smooth(colour = "#000004FF", fill = "#FCFDBFFF", size = .7) +
  labs(x = "Appreciation for News Selector", 
       y = "Levels of Trust in Media",
       title = "Bivariate Relationship") +
  facet_wrap(.~name, ncol = 2, scales = "free") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())

```

```{r}
Ht1 <- lm(own_select ~ esc + ent + hs + pt + surv +
           eo + factor(missing_eo) + news + polef + trust +
           age + factor(gender) + factor(country),  data = df)

Ht2 <- lm(jou_select ~ esc + ent + hs + pt + surv +
           eo + factor(missing_eo) + news + polef + trust +
           age + factor(gender) + factor(country),  data = df)

Ht3 <- lm(trust ~ own_select + jou_select + eo +
          factor(missing_eo) + news + polef + age + 
          factor(gender) + factor(country),  data = df)

#stargazer::stargazer(Ht1, Ht2, Ht3,
#                     type = "latex", title="Results", align=TRUE,
#                     star.char = c("+", "*", "**", "***"),
#                     star.cutoff = c(.1, .05, .01, .001),
#                     dep.var.labels = c("Self-Selection", "Journalist Select", 
#                                        "Trust in Media"),  
#          covariate.labels = c("UGT: Escapism", "UGT: Entertainment", 
#                               "UGT: Habit Strength", "UGT: Passing Time", 
#                               "UGT: Surveillance", "Epistemic Overconfidence (EO)",
#                               "Missing Values: EO", "News Usage", 
#                               "Political Efficacy", "Trust in Media",
#                               "Age", "Gender: Male", "Country: US"))
```

```{r, echo=F}
tmp <- Ht1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght",
                       "UGT: Passing Time", 
                       "UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                        "Age","Gender: Male",
                       "Country: US"),
         id = "DV: I select my own news") %>%
  select(-term)

Ht2  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght",
                       "UGT: Passing Time", 
                       "UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", 
                       "Trust in Media",
                        "Age","Gender: Male",
                       "Country: US"),
         id = "Let journalist choose news for me") %>%
  select(-term) %>%
  add_row(tmp) %>%
  ggplot(aes(y = variable)) +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(Ht1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  facet_grid(.~id, scales = "free") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
rm(tmp, Ht1, Ht2)

Ht3  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("I select my own news",
                       "Let journalist select my news",
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values",
                       "News Usage", "Political Efficacy", 
                        "Age","Gender: Male",
                       "Country: US")) %>%
  select(-term) %>%
  ggplot(aes(y = variable)) +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(Ht3), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "", title = "DV: Trust in Media") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5))
rm(tmp, Ht1, Ht2, Ht3)
```

### Relationship between Appreciation for Journalists as News Selectors and Overconfidence

```{r}
Hj1 <-  lm(jou_select ~ esc *eo + ent + hs + pt + surv +
            missing_eo + news + polef + trust + age +
            factor(gender) + factor(country),  data = df)

Hj2 <-  lm(jou_select ~ esc + ent*eo + hs + pt + surv +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

Hj3 <-  lm(jou_select ~ esc + ent + hs*eo + pt + surv +
              factor(missing_eo) + news + polef + trust +
              age + factor(gender) + factor(country),  data = df)

Hj4 <-  lm(jou_select ~ esc + ent + hs + pt*eo + surv +
              factor(missing_eo) + news + polef + trust + 
              age + factor(gender) + factor(country),  data = df)

Hj5 <-  lm(jou_select ~ esc + ent + hs + pt + surv*eo +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

#stargazer::stargazer(Hj1, Hj2, Hj3, Hj4, Hj5,
#                     type = "latex", title="Results", align=TRUE,
#                     star.char = c("+", "*", "**", "***"),
#                     star.cutoff = c(.1, .05, .01, .001),
#                     dep.var.labels = c("Appreciation for Journalists Selectors"),  
#          covariate.labels = c("UGT: Escapism", "UGT: Entertainment", 
#                               "UGT: Habit Strength", "UGT: Passing Time", 
#                               "UGT: Surveillance", "Epistemic Overconfidence (EO)",
#                               "Missing Values: EO", "News Usage", 
#                               "Political Efficacy", "Trust in Media",
#                               "Age", "Gender: Male", "Country: US", 
#                               "Interaction UGT * EO"))
```

```{r, echo=F, fig.width=10, fig.height=10}
f2_1 <- Hj1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "Epistemic Overconfidence", 
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Escapism * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_2 <- Hj2  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment",
                       "Epistemic Overconfidence", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Entertainment * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_3 <- Hj3  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "Epistemic Overconfidence",
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Habit Strength * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_4 <- Hj4  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time",
                       "Epistemic Overconfidence","UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Passing Time * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_5 <- Hj5  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time","UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Surveillance * Epistemic Overconfidence", 14)) %>%
  select(-term)

rbind(f2_1, f2_2, f2_3, f2_4, f2_5) %>%
  ggplot(aes(y = variable)) +
  facet_wrap(~ id, ncol = 2, scales = "free") +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(Hj1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  ggtitle("DV: Appreciation for Journalists as News Selectors") +
  theme(plot.title = element_text(hjust = 0.5))
rm(f2_1, f2_2, f2_3, f2_4, f2_5)
```

### Predicted Effects
```{r, echo=FALSE,fig.width=10, fig.height=10}
mg1 <- ggpredict(Hj1, terms = c("esc[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Escapism")
mg2 <- ggpredict(Hj2, terms = c("ent[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Entertainment")
mg3 <- ggpredict(Hj3, terms = c("hs[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Habit Strength")
mg4 <- ggpredict(Hj4, terms = c("pt[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Passing Time")
mg5 <- ggpredict(Hj5, terms = c("surv[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Surveillance")

rbind(mg1, mg2, mg3, mg4, mg5) %>%
  mutate(group = recode(group, 
                        `-1` = "Insecure",
                        `2` = "Not Overconfident",
                        `4` = "Overconfident")) %>%
  ggplot(aes(x = x, y = predicted, colour = group)) +
  geom_line() +
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill = group), alpha=0.15) +
  labs(x = "Levels of Gratifications of the News", 
       y = "Predicted Effects on DV for Levels of Overconfidence",
       title = "DV: Appreciation for Journalists as News Selector") +
  facet_wrap(.~id, ncol = 2, scales = "free") +
  theme_minimal() +
  scale_fill_viridis(option = "magma", discrete = T) +
  scale_color_viridis(option = "magma", discrete = T) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())
rm(Hj1, Hj2, Hj3, Hj4, Hj5, 
   mg1, mg2, mg3, mg4, mg5)
```

### Relationship between Appreciation for Self Selecting the News and Overconfidence

```{r}
Hs1 <-  lm(own_select ~ esc *eo + ent + hs + pt + surv +
            missing_eo + news + polef + trust + age +
            factor(gender) + factor(country),  data = df)

Hs2 <-  lm(own_select ~ esc + ent*eo + hs + pt + surv +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

Hs3 <-  lm(own_select ~ esc + ent + hs*eo + pt + surv +
              factor(missing_eo) + news + polef + trust +
              age + factor(gender) + factor(country),  data = df)

Hs4 <-  lm(own_select ~ esc + ent + hs + pt*eo + surv +
              factor(missing_eo) + news + polef + trust + 
              age + factor(gender) + factor(country),  data = df)

Hs5 <-  lm(own_select ~ esc + ent + hs + pt + surv*eo +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

#stargazer::stargazer(Hs1, Hs2, Hs3, Hs4, Hs5,
#                     type = "latex", title="Results", align=TRUE,
#                     star.char = c("+", "*", "**", "***"),
#                     star.cutoff = c(.1, .05, .01, .001),
#                     dep.var.labels = c("Appreciation for Self-Selection"),  
#          covariate.labels = c("UGT: Escapism", "UGT: Entertainment", 
#                               "UGT: Habit Strength", "UGT: Passing Time", 
#                               "UGT: Surveillance", "Epistemic Overconfidence (EO)",
#                               "Missing Values: EO", "News Usage", 
#                               "Political Efficacy", "Trust in Media",
#                               "Age", "Gender: Male", "Country: US", 
#                               "Interaction UGT * EO"))
```

```{r, echo=F, fig.width=10, fig.height=10}
f2_1 <- Hs1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "Epistemic Overconfidence", 
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Escapism * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_2 <- Hs2  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment",
                       "Epistemic Overconfidence", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Entertainment * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_3 <- Hs3  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "Epistemic Overconfidence",
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Habit Strength * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_4 <- Hs4  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time",
                       "Epistemic Overconfidence","UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Passing Time * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_5 <- Hs5  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time","UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Surveillance * Epistemic Overconfidence", 14)) %>%
  select(-term)

rbind(f2_1, f2_2, f2_3, f2_4, f2_5) %>%
  ggplot(aes(y = variable)) +
  facet_wrap(~ id, ncol = 2, scales = "free") +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(Hs1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  ggtitle("DV: Appreciation for Self Selecting") +
  theme(plot.title = element_text(hjust = 0.5))
rm(f2_1, f2_2, f2_3, f2_4, f2_5)
```

### Predicted Effects
```{r, echo=FALSE,fig.width=10, fig.height=10}
mg1 <- ggpredict(Hs1, terms = c("esc[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Escapism")
mg2 <- ggpredict(Hs2, terms = c("ent[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Entertainment")
mg3 <- ggpredict(Hs3, terms = c("hs[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Habit Strength")
mg4 <- ggpredict(Hs4, terms = c("pt[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Passing Time")
mg5 <- ggpredict(Hs5, terms = c("surv[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Surveillance")

rbind(mg1, mg2, mg3, mg4, mg5) %>%
  mutate(group = recode(group, 
                        `-1` = "Insecure",
                        `2` = "Not Overconfident",
                        `4` = "Overconfident")) %>%
  ggplot(aes(x = x, y = predicted, colour = group)) +
  geom_line() +
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill = group), alpha=0.15) +
  labs(x = "Levels of Gratifications of the News", 
       y = "Predicted Effects on DV for Levels of Overconfidence",
       title = "DV: Appreciation for Self Selecting") +
  facet_wrap(.~id, ncol = 2, scales = "free") +
  theme_minimal() +
  scale_fill_viridis(option = "magma", discrete = T) +
  scale_color_viridis(option = "magma", discrete = T) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())
rm(Hs1, Hs2, Hs3, Hs4, Hs5, 
   mg1, mg2, mg3, mg4, mg5)
```