---
title: 'Analysis for Epistemic Overconfidence in Algorithmic News Selection Paper'
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(printr)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Load Data](#load-data)
- [Analysis](#analysis)
  - [H1: Direct Effect of UGT on Algorithmic Appreciation](#h1:-direct-effect-of-ugt-on-algorithmic-appreciation)
  - [H2: Interaction UGT * Epistemic Overconfidence](#h2:-interaction-ugt-*-epistemic-overconfidence)
  - [Predicted Effects](#predicted-effects)

## Required Packages &amp; Reproducibility
```{r, message=FALSE, warning=F}
rm(list=ls())

renv::snapshot()

source("../lib/functions.R")
```

## Load Data
```{r}
load("../../data/intermediate/cleaned_data.RData") 
df <- df %>%
  mutate(esc = round(esc, 0),
         ent = round(ent, 0),
         hs = round(hs, 0),
         pt = round(pt, 0),
         surv = round(surv, 0))
#  pid = factor(pid, levels = c("None", "Other", "Democrat",
#                                      "Republican")))
```

## Analysis

### H1: Direct Effect of UGT on Algorithmic Appreciation
```{r}
#df <- within(df, pid <- relevel(pid, ref = "Other"))
H1 <- lm(algo_app ~ esc + ent + hs + pt + surv +
           eo + factor(missing_eo) + news + polef + trust +
           age + factor(gender) + factor(country),  data = df)
```

```{r, echo=F}
H1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght",
                       "UGT: Passing Time", 
                       "UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                        "Age","Gender: Male",
                       "Country: US")) %>%
  select(-term) %>%
  ggplot(aes(y = variable)) +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(H1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  ggtitle("DV: Algorithmic Appreciation") +
  theme(plot.title = element_text(hjust = 0.5))
rm(H1)
```

### H2: Interaction UGT * Epistemic Overconfidence

```{r}
#H2 Interaction Effect Epistemic Overconfidence
H2_1 <-  lm(algo_app ~ esc *eo + ent + hs + pt + surv +
            missing_eo + news + polef + trust + age +
            factor(gender) + factor(country),  data = df)

H2_2 <-  lm(algo_app ~ esc + ent*eo + hs + pt + surv +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)

H2_3 <-  lm(algo_app ~ esc + ent + hs*eo + pt + surv +
              factor(missing_eo) + news + polef + trust +
              age + factor(gender) + factor(country),  data = df)

H2_4 <-  lm(algo_app ~ esc + ent + hs + pt*eo + surv +
              factor(missing_eo) + news + polef + trust + 
              age + factor(gender) + factor(country),  data = df)

H2_5 <-  lm(algo_app ~ esc + ent + hs + pt + surv*eo +
              factor(missing_eo) + news + polef + trust + age +
              factor(gender) + factor(country),  data = df)
```

```{r, echo=F, fig.width=10, fig.height=10}
f2_1 <- H2_1  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "Epistemic Overconfidence", 
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Escapism * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_2 <- H2_2  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment",
                       "Epistemic Overconfidence", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Entertainment * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_3 <- H2_3  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "Epistemic Overconfidence",
                       "UGT: Passing Time", "UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Habit Strength * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_4 <- H2_4  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time",
                       "Epistemic Overconfidence","UGT: Surveillance", 
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Passing Time * Epistemic Overconfidence", 14)) %>%
  select(-term)

f2_5 <- H2_5  %>%
  broom::tidy() %>%
  filter(term != "(Intercept)") %>%
  mutate(variable =  c("UGT: Escapism",
                       "UGT: Entertainment", 
                       "UGT: Habit Strenght", 
                       "UGT: Passing Time","UGT: Surveillance", 
                       "Epistemic Overconfidence",
                       "Epistemic Overconfidence: Missing Values", 
                       "News Usage", "Political Efficacy", "Trust in Media",
                       "Age","Gender: Male", "Country: US",
                       "Interaction"),
         id = rep("Surveillance * Epistemic Overconfidence", 14)) %>%
  select(-term)

rbind(f2_1, f2_2, f2_3, f2_4, f2_5) %>%
  ggplot(aes(y = variable)) +
  facet_wrap(~ id, ncol = 2, scales = "free") +
  stat_dist_halfeyeh(aes(dist = "student_t", arg1 = df.residual(H2_1), 
                         arg2 = estimate, arg3 = std.error))  +
  labs(x = "", y = "") +
  geom_vline(xintercept = 0, size = .5) +
  theme_minimal() +
  ggtitle("DV: Algorithmic Appreciation") +
  theme(plot.title = element_text(hjust = 0.5))
rm(f2_1, f2_2, f2_3, f2_4, f2_5)
```

### Predicted Effects
```{r, echo=FALSE,fig.width=10, fig.height=10}
mg1 <- ggpredict(H2_1, terms = c("esc[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Escapism")
mg2 <- ggpredict(H2_2, terms = c("ent[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Entertainment")
mg3 <- ggpredict(H2_3, terms = c("hs[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Habit Strength")
mg4 <- ggpredict(H2_4, terms = c("pt[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Passing Time")
mg5 <- ggpredict(H2_5, terms = c("surv[1:7]", "eo[-1, 2,4]")) %>%
  mutate(id = "Surveillance")

rbind(mg1, mg2, mg3, mg4, mg5) %>%
  mutate(group = recode(group, 
                        `-1` = "Insecure",
                        `2` = "Not Overconfident",
                        `4` = "Overconfident")) %>%
  ggplot(aes(x = x, y = predicted, colour = group)) +
  geom_line() +
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill = group), alpha=0.15) +
  labs(x = "Levels of Gratifications of the News", 
       y = "Predicted Effects on DV for Levels of Overconfidence",
       title = "DV: Algorithmic Appreciation") +
  facet_wrap(.~id, ncol = 2, scales = "free") +
  theme_minimal() +
  scale_fill_viridis(option = "magma", discrete = T) +
  scale_color_viridis(option = "magma", discrete = T) +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank())
```